City-GAN: Learning architectural styles using a custom Conditional GAN architecture

### 2020-05-26 paper/paper.tex
Update paper

\begin{figure}
\includegraphics[width=\columnwidth]{figures/architectures/maxnet_final.pdf}
\caption{The architecture of our neural network is inspired by \cite{pytorch_deep_2019}. The difference in our custom architecture is that labels are fed into the generator (top) as well as into the discriminator (bottom) alongside the data.}  % TODO
\label{fig:maxnet}
\end{figure}

@@

Finally, we wanted to investigate whether a larger dataset could significantly improve the quality of generated images. For this we used a dataset of Stanford University \citep{pytorch_deep_2019} and extracted 500,000 images for the cities of Amsterdam, Washington DC, Florence, Las Vegas and Manhattan. These images are not curated, thus it is not guaranteed that they actually show facades.

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{figures/architectures/maxnet.pdf}
\caption{The architecture of our neural network is inspired by \cite{pytorch_deep_2019}. The difference in our custom architecture is that labels are fed into the generator (top) as well as into the discriminator (bottom) alongside the data.}  % TODO
\label{fig:maxnet}
\end{figure}

@@

Finally, we wanted to investigate whether a larger dataset could significantly improve the quality of generated images. For this we used a dataset of Stanford University \citep{zamir_repo_2019} and extracted 500,000 images for the cities of Amsterdam, Washington DC, Florence, Las Vegas and Manhattan. These images are not curated, thus it is not guaranteed that they actually show facades.
